---
title: "Intro to shiny"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: true
    highlight: tango
    theme: flatly
    df_print: paged
    self_contained: true
---

```{r setup, include=FALSE}
library(tidyverse)
fs::dir_create("www")
knitr::opts_chunk$set(
    echo = TRUE,
    fig.path = "www")
```

This document outlines the applications in the posit.cloud workspace for the LA County Department of Public Health shiny training.

## 1. `basic/` shiny app

This basic shiny app gives an overview of the `fluidPage()` layout functions, inputs, outputs, and reactives.

```{r basic, echo=FALSE}
fs::dir_tree("basic")
```

The `basic.R` file contains an empty application, solution.R contains the worked solution from the slides (`intro-to-shiny.pdf`)

## 2. `sidebar/` app

```{r sidebar, echo=FALSE}
fs::dir_tree("sidebar")
```

This folder contains another version of `My App`, but without the reactive expression.

## 3. `tables/` shiny app

The `tables` shiny app gives an overview of various table outputs in shiny (also shows how to use the `shiny::observeEvent()` function)

```{r tables, echo=FALSE}
fs::dir_tree("tables")
```

## 4. `graphs/` shiny app

This application shows how write plotting functions for shiny apps (using `rlang` and other meta-programming methods.

```{r graphs, echo=FALSE}
fs::dir_tree("graphs")
```

## 5. `reactlog/` shiny app

Open the `reactlog.R` file.

```{r reactlog-no-recurse, echo=FALSE}
fs::dir_tree("reactlog/", recurse = FALSE)
```

Inside the `reactlog/` folder there are two apps: `reactives/reactive.R` and `reactives/nonreactive.R`.

```{r reactlog-apps, echo=FALSE}
fs::dir_tree("reactlog/reactives/")
```

Follow the instructions in `reactlog.R` to use the `reactlog` package.

## 6. `gtrends/` shiny app

This application creates an application using the `gtrendsR` package.

```{r gtrends, echo=FALSE}
fs::dir_tree("gtrends/")
```

The application loads two datasets in `data/`

```{r gtrends-data, echo=FALSE}
fs::dir_tree("gtrends/data")
```

These data were scraped on 2022-12-15.

## 7. `navbar/` shiny app

The navbar app contains the `navbarPage()` functions

```{r navbar-page, echo=FALSE}
fs::dir_tree("navbar/")
```
